On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
sml edts

We remark that these results have a strong application to theoretical neuroscience, justifying what may be the first hypothesized theory of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.

\begin{corollary}
Random noisy (linear) compression of sparse neural activities $\mathbf{x}_i$ is decompressible by any neurally plausible unsupervised sparse feature learning algorithm.
\end{corollary}

>>>>

We remark that these results have a strong application to theoretical neuroscience, mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10, ganguli2012compressed}.

\begin{corollary}
Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm.
\end{corollary}
